---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Julian Carrasquillo"
date: "8/26/2019"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

According to the helpfile, the datasaurus_dozen dataset has 1,846 records and 3 variables - x, y, and dataset.

### Exercise 2

First let's plot the data in the **dino** dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Ok, let's try this again for the **star** dataset!

```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

It looks like we have very similar correlation stats, but very different observations.

### Exercise 4

Ok, let's try this again for the **circle** dataset!

```{r plot-star, fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-star}
circle_data %>%
  summarize(r = cor(x, y))
```

Again, we've got similar correlation stats, but very different observations when graphed.

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)